%-------------------------
% CV in Latex
% Author : James Yu
% Based off of: https://github.com/jakegut/resume and https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}



% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{.75in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
%-------------------------

% Heading
\newcommand{\cvProjectSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% Subheading with SubSubheading
\newcommand{\cvSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

% Subheading without SubSubheading
\newcommand{\cvSingleSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% Research Subheading
\newcommand{\cvResearchSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 \\
      \small #4 & \textit{\small #5} \\
    \end{tabular*}\vspace{-7pt}
}

% Additional SubSubheading
\newcommand{\cvSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% Additional Research SubSubheading
\newcommand{\cvResearchSubSubheading}[2]{
    \vspace{-6pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}



% line item/bullet point
\newcommand{\cvItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% SubItem
\newcommand{\cvSubItem}[1]{\cvItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\cvSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\cvSubHeadingListEnd}{\end{itemize}}
\newcommand{\cvItemListStart}{\begin{itemize}}
\newcommand{\cvItemListEnd}{\vspace{-5pt}\end{itemize}}
\newcommand{\cvPubListStart}{\begin{enumerate}[labelindent=0.15in, itemsep=0pt]}
\newcommand{\cvPubListEnd}{\vspace{-5pt}\end{enumerate}}



%-------------------------------------------
%           CV STARTS HERE  
%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape James Yu} \\ \vspace{1pt}
    123 Main Street, City, State Zip

    \small 123-346-7890 
    $|$ \href{mailto:john.doe@x.edu}{\underline{\smash{john.doe@x.edu}}} 
    $|$ \href{linkedin.com/in/james-yu-b8883491/}{\underline{\smash{LinkedIn}}} 
    % $|$ \href{https://github.com/jyprojs}{\underline{\smash{GitHub}}}
    \vspace{-15pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \cvSubHeadingListStart
    \cvSubheading
      {Case Western Reserve University School of Medicine}{Cleveland, OH}
      {Doctor of Medicine -- expected}{July 2017 -- May 2022}
    \cvSubheading
      {John Hopkins University Whiting School of Engineering}{Baltimore, MD}
      {Masters of Science in Computer Science -- expected}{Aug. 2020 -- May 2022}
    \cvItemListStart
        \cvItem{Relevant coursework: Applied Machine Learning, Neural Networks}
    \cvItemListEnd
    \cvSubheading
      {University of California, Riverside}{Riverside, CA}
      {Bachelor of Science in Biochemistry}{Aug. 2012 -- May 2015}
      \cvItemListStart
        \cvItem{Medical Sciences Emphasis}
        \cvItem{graduated \textit{magna cum laude}}
    \cvItemListEnd
  \cvSubHeadingListEnd


%------HONORS AND AWARDS--------
\section{Honors and awards}
\cvSubHeadingListStart
    \cvSingleSubheading
      {\textbf{Certificate of Completion}} {May 2020}{}{}
        \cvItemListStart
            \cvItem{Health Systems Science: Application to Patient Care Quality Improvement Charter and Reflective Blogs}
            \cvItem{Top 10\% of reflective Blogs}
        \cvItemListEnd
    \cvSingleSubheading
      {\textbf{Dr. Thomas Halsey Chancellor’s Scholarship/ Chancellor’s Scholarship}}{2012-2015}{}{}
    \cvSingleSubheading
      {\textbf{Chancellor’s Honor List}}{2012-2013, 2014-2015}{}{}
\cvSubHeadingListEnd

%--------WORK EXPERIENCE---------
\section{Work Experience}
  \cvSubHeadingListStart
    \cvSubheading
      {Emergency Medical Technician}{Gardena, CA}
      {Ambuserve Ambulance Services}{Feb. 2016 -- May 2016}
      \cvItemListStart
        \cvItem{Gave and received patient care reports, documented patient encounters, and provided care to patients in route}
      \cvItemListEnd
  \cvSubHeadingListEnd

%-------RESEARCH EXPERIENCE---------
\section{Research Experience}
  \cvSubHeadingListStart
    \cvResearchSubheading
      {UH Cleveland Medical Center, Division of Pediatric Orthopaedic Surgery}{Cleveland, OH}
      {PI: Dr. R. Justin Mistovich}
      {Project: Conservative treatment outcomes for post-operative seromas in pediatric scoliosis patients}{2018 -- 2019}
      \cvItemListStart
        \cvItem{Collected descriptive statistics on case series of post-operative seromas following posterior spinal fusion surgeries}
        \cvItem{Conducted literature search on post-operative seromas after spinal surgery.}
        \cvItem{Primary authorship of peer-reviewed publication and poster at national conference.}
      \cvItemListEnd
    \cvResearchSubSubheading
      {Project: Long-term outcomes of growth-friendly implants in EOS patients following deep SSIs}{2018 -- present}
      \cvItemListStart
        \cvItem{Use of R and Excel for data analysis, tables and figures.}
        \cvItem{Literature review, authorship and editing of manuscript.}
        \cvItem{Culminated in podium presentation and manuscript submission}
      \cvItemListEnd

    \cvResearchSubheading
      {Louis Stokes Cleveland VA Medical Center, Advanced Platform Technology}{Cleveland, OH}
      {PI: Dr. Triolo Ph.D.}
      {Project: Use of electrical stimulation to restore sensation in lower limb amputees}{2018 -- 2019}
      \cvItemListStart
        \cvItem{Advised in experimentation to study the relationship between electrical-stimulation-induced-sensations and EMG activity in lower limb muscles.}
        \cvItem{Conducted literature search for study design.}
        \cvItem{Authorship and editing of peer-reviewed publication and poster at a national conference.}
      \cvItemListEnd
    \cvResearchSubheading
      {Medical College of Wisconsin, Department of Medicine}{Milwaukee, WI}
      {PI: Jyoti Sengupta Ph.D. and Banani Banerjee Ph.D.}
      {Project: Neuromolecular Mechanisms of Chronic Pelvic Pain in Neonatally-induced Cystitis}{2016 -- 2017}
      \cvItemListStart
        \cvItem{Survival surgeries: intrathecal catheterization and EMG electrodes implantation in SD rats}
        \cvItem{Behavior studies: visceromotor response to colorectal distension and von Frey filament test in neonatally-induced cystitis models.}
        \cvItem{Molecular experiments: analysis of microRNA and protein (mir92b, KCC2, VGAT) expression through RT- PCR and Western Blot repectively}
        \cvItem{Use of Excel, CorelDraw, SigmaPlot, EndNote for figures, graphs, statistics and references.}
        \cvItem{Contributed in authorship and editing of peer-reviewed publication.}
      \cvItemListEnd
  \cvSubHeadingListEnd



%-----PEER-REVIEWED PUBLICATIONS-----
\section{Peer-Reviewed Publications}
  \cvPubListStart
    \small{
    \item Dumaine AM, \textbf{Yu J}, Poe-Kochert C, Thompson GH, Mistovich RJ. ``Surgical Site Infections in Early Onset Scoliosis What Are Long-term Outcomes and Predictors of Success?” Spinal Deformity \textit{ --- under Revision; April 2021 }

    \item  \textbf{Yu J}, Dumaine AM, Poe-Kochert C, Thompson GH, Mistovich RJ. ``Seromas Following Pediatric Spinal Deformity Surgery: Is Operative Management Necessary?" J Pediatr Orthop. 2019 Dec 23. doi: 10.1097/BPO.0000000000001496. PubMed PMID: 31876697.
    
    \item Cheng K, Charkhkar H, \textbf{Yu J}, Makowski N, Triolo R. ``Probing peripheral neural pathways in electrically stimulation induced sensation," 2019 9th International IEEE/EMBS Conference on Neural Engineering (NER), San Francisco, CA, USA, 2019, pp. 453-456. Published on IEEE Xplore
    
    \item  Zhang J, \textbf{Yu J}, Kannampalli P, Nie L, Meng H, Medda B, Shaker R, Sengupta JN, Banerjee B. ``miRNAmediated downregulation of KCC2 and VGAT expression in spinal cord contributes to neonatal cystitis-induced visceral pain in rats.” Pain. 2017 Sep 1. doi: 10.1097/j.pain.0000000000001057. PMID: 28885452.
    }
  \cvPubListEnd
    

%-----POSTER & PODIUM PRESENTATIONS------
\section{Poster \& Podium Presentations}
  \cvPubListStart
    \small{
    \item Dumaine AM, \textbf{Yu J}, Poe-Kochert C, Thompson GH, Mistovich RJ. “Long Term Outcomes Following Surgical Site Infections in Early Onset Scoliosis Patients: A 15-year Retrospective Review.” American Academy of Pediatrics Virtual National Conference \& Exhibition. October 2020.
    
    \item  \textbf{Yu J}, Dumaine AM, Poe-Kochert C, Thompson GH, Mistovich RJ. “Seromas following Pediatric Spinal Deformity Surgery: Is Operative Management Necessary?” Mid-America Orthopaedic Association 38th Annual Meeting. April 2020.
    
    \item Zhang J, \textbf{Yu J}, Meng H, Kannampalli P, Medda B, Shaker R, Sengupta JN, Banerjee B. “MicroRNA-mediated downregulation of GABA-associated co-transporter and transporter in rats spinal dorsal horns with zymosan-induced cystitis” MCW Department of Medicine Retreat; Milwaukee, WI (2017).
    }
  \cvPubListEnd

%-----------PROJECTS-----------
% \section{Projects}
%   \cvSubHeadingListStart
%     \cvProjectSubheading
%     {\textbf{Patentpy/Patentr} $|$ \emph{Python, TravisCI, codecov, Git}}{June 2020 -- Present}
%       \cvItemListStart
%         \cvItem{Developed a PyPI python package to convert bulk patent data from TXT and XML to csv/dataframe format from USPTO bulk patent website.}
%         \cvItem{Utilized Pybind11 to wrap custom C++ code for parsing relevant fields from TXT formatted files.}
%         \cvItem{Streamlined updates through use of CI tools, TravisCI and codecov, and pytest-cov for testing.}
%         \cvItem{Wrote detailed documentation via Sphinx and hosted it on GitHub Pages.}
%         \cvItem{Contributed to CRAN R package counterpart}
%       \cvItemListEnd
%   \cvSubHeadingListEnd


%--------COMMUNITY SERVICE---------
\section{Community Service}
  \cvSubHeadingListStart
    \cvSubheading
    {Riverside Community Hospital}{Riverside, CA}
    {Volunteer}{2014 -- 2015}
      \cvItemListStart
         \cvItem{Escorted patients and visitors throughout hospital; delivered mail, gifts, and flowers; and helped to discharge patients.}
      \cvItemListEnd
      
    \cvSubheading{Medical Students Cultural Exchange}{New Taipei, Taiwan}{Teaching Assistant and Facilitator}{Summer 2015}
      \cvItemListStart
         \cvItem{Facilitated group discussions and helped coordinated summer camp activities with Taiwanese medical students.}
         \cvItem{Gave presentation on Patient Protection and Affordable Care Act.}
      \cvItemListEnd
  \cvSubHeadingListEnd

%-------------LANGUAGES----------------
\section{Languages}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{English}{: Fluent} \\
      \textbf{Mandarin}{: Proficient} \\
    }}
    \vspace{-3pt}
  \end{itemize}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Programming Languages}{: Python, JavaScript, C++, HTML/CSS, R} \\
      \textbf{Developer Tools}{: Git, Docker, TravisCI, VS Code} \\
      \textbf{Libraries}{: pandas, NumPy, Matplotlib, seaborn, sklearn, pytest-cov, pybind11, Sphinx}
    }}
  \end{itemize}
 



%-------------------------------------------
\end{document}
